tl20-05_berghei_pir_DESEQ

### 2021-10-01 chapter3_results_bergheiPir/Manuscript_berghei_pir_DESEQ.Rmd
Save deseq stats

```{r save_stats_df}
sig_pirs_cast

write_xlsx(deseq_stats, 
           'SupplementaryInformation4_Stats_DESEQ_berghei.xlsx')
write.csv(deseq_stats, 
           'SupplementaryInformation4_Stats_DESEQ_berghei.csv')
# deseq_stats <- read.csv('SupplementaryInformation4_Stats_DESEQ_berghei.csv',
#                         row.names = 1)
```

>>>>

```{r save_stats_df}
deseq_stats <- bind_rows(shrunk.list) %>% 
  mutate(subfam = pir_clade$clade[match(Geneid, pir_clade$Geneid)]) %>% 
  arrange(subfam, Geneid)

write_xlsx(deseq_stats, 
           'SupplementaryInformation4_Stats_DESEQ_berghei.xlsx')
write.csv(deseq_stats, 
           'SupplementaryInformation4_Stats_DESEQ_berghei.csv')
